---
title: "CY2025 Bridge Year Projections"
format: 
  html:
    page-layout: full
    toc: true
    toc-location: left
editor: visual
embed-resources: true
execute: 
  echo: false
  message: false
  warning: false
---

```{r}
#|label: "run projections and make table"
library(ggplot2)
library(dplyr)
library(tidyverse)
library(htmltools)
library(lubridate)
data <- readRDS(file = "output/catch_proj_data.rds")
`%!in%` <- Negate(`%in%`)
source("R/simple_projection_fnc.R")

stock <- unique(data$STOCK_ID)


for (i in 1:length(stock)) {

  data_stock <- filter(data, STOCK_ID == stock[i])
  fishery_group <- unique(data_stock$FISHERY_GROUP)

  for (j in 1:length(fishery_group)) {

    assign(paste0(stock[i],"_",fishery_group[j]), simple_projection(data = data_stock, stock = stock[i], fishery_group = fishery_group[j], start_date = '2025-06-01'))


  }

}
```

# Projection Table

```{r}
table <- data.frame(stock = "GOM Yellowtail",
                    total_catch = YELCCGM_SECT$final_MT + YELCCGM_CP$final_MT + YELCCGM_STATE$final_MT + YELCCGM_OTHER$final_MT,
                    groundfish = YELCCGM_SECT$final_MT + YELCCGM_CP$final_MT,
                    sector = YELCCGM_SECT$final_MT,
                    common_pool = YELCCGM_CP$final_MT,
                    rec = '-',
                    scallop = 'NA*',
                    small_mesh = 'NA*',
                    state = YELCCGM_STATE$final_MT,
                    other = YELCCGM_OTHER$final_MT) |>
  rbind(data.frame(stock = "GB Yellowtail",
                    total_catch = YELGB_GROUND$final_MT + `YELGB_SQUID/WHITING`$final_MT + YELGB_SCALLOP$final_MT + YELGB_OTHER$final_MT,
                    groundfish = YELGB_GROUND$final_MT,
                    sector = 'NA**',
                    common_pool = 'NA**',
                    rec = '-',
                    scallop = YELGB_SCALLOP$final_MT,
                    small_mesh = `YELGB_SQUID/WHITING`$final_MT,
                    state = "NA",
                    other = YELGB_OTHER$final_MT)) |>
  rbind(data.frame(stock = "SNE Yellowtail",
                   total_catch = YELSNE_CP$final_MT + YELSNE_SECT$final_MT + YELSNE_SCALLOP$final_MT + YELSNE_STATE$final_MT + YELSNE_OTHER$final_MT, 
                   groundfish =  YELSNE_CP$final_MT + YELSNE_SECT$final_MT,
                   sector = YELSNE_SECT$final_MT,
                   common_pool = YELSNE_CP$final_MT,
                   rec = '-',
                   scallop = YELSNE_SCALLOP$final_MT,
                   small_mesh = "NA*",
                   state = YELSNE_STATE$final_MT,
                   other = YELSNE_OTHER$final_MT)) |>
  rbind(data.frame(stock = "GB Winter Flounder",
                   total_catch = FLWGB_GROUND$final_MT + FLWGB_OTHER$final_MT, 
                   groundfish =  FLWGB_GROUND$final_MT,
                   sector = "NA**",
                   common_pool = "NA**",
                   rec = '-',
                   scallop = "NA*",
                   small_mesh = "NA*",
                   state = "NA",
                   other = FLWGB_OTHER$final_MT)) |>
  rbind(data.frame(stock = "SNEMA Winter Flounder",
                   total_catch = FLWSNEMA_CP$final_MT + FLWSNEMA_OTHER$final_MT + FLWSNEMA_SECT$final_MT + FLWSNEMA_STATE$final_MT, 
                   groundfish = FLWSNEMA_CP$final_MT + FLWSNEMA_SECT$final_MT,
                   sector = FLWSNEMA_SECT$final_MT,
                   common_pool = FLWSNEMA_CP$final_MT,
                   rec = '*',
                   scallop = "NA*",
                   small_mesh = "NA*",
                   state = FLWSNEMA_STATE$final_MT,
                   other =  FLWSNEMA_OTHER$final_MT)) |> 
  rbind(data.frame(stock = "White Hake",
                   total_catch = HKWGMMA_CP$final_MT + HKWGMMA_OTHER$final_MT + HKWGMMA_SECT$final_MT + HKWGMMA_STATE$final_MT,
                   groundfish = HKWGMMA_CP$final_MT + HKWGMMA_SECT$final_MT,
                   sector = HKWGMMA_SECT$final_MT,
                   common_pool = HKWGMMA_CP$final_MT,
                   rec = '-',
                   scallop = "NA*",
                   small_mesh = "NA*",
                   state = HKWGMMA_STATE$final_MT,
                   other =  HKWGMMA_OTHER$final_MT)) |>
  rbind(data.frame(stock = "Redfish",
                   total_catch = REDGMGBSS_CP$final_MT + REDGMGBSS_OTHER$final_MT + REDGMGBSS_SECT$final_MT + REDGMGBSS_STATE$final_MT,
                   groundfish = REDGMGBSS_CP$final_MT + REDGMGBSS_SECT$final_MT,
                   sector = REDGMGBSS_SECT$final_MT,
                   common_pool = REDGMGBSS_CP$final_MT,
                   rec = '-',
                   scallop = "NA*",
                   small_mesh = "NA*",
                   state = REDGMGBSS_STATE$final_MT,
                   other =  REDGMGBSS_OTHER$final_MT))

DT::datatable(table,
              caption = htmltools::tags$caption("* - Recreational and Canada Landings Data are based on average of three previous calendar years",
  tags$br(),
  "NA* - When no sub-ACL is allocated, component is part of 'other' category",
  tags$br(),
  "NA** - Sector and Common Pool values combined for confidentiality"),
    extensions = 'Buttons',
    options = list(
                                paging = TRUE,
                                searching = TRUE,
                                fixedColumns = TRUE,
                                autoWidth = TRUE,
                                ordering = TRUE,
                                dom = 'tB',
                                buttons = c('copy', 'csv', 'excel'))) # Inserts a line break


```

Methods: Calendar 2024 catch data are scaled using the mean difference in catch from CY24 to CY25 over the period June 1st - July 14th.

## GOM Yellowtail Flounder

### Sector

```{r}
YELCCGM_SECT$plot
```

### Common Pool

```{r}
YELCCGM_CP$plot
```

### State

```{r}
YELCCGM_STATE$plot
```

### Other

```{r}
YELCCGM_OTHER$plot
```

# GB Yellowtail

### Groundfish

```{r}
YELGB_GROUND$plot
```

### Scallop

```{r}
YELGB_SCALLOP$plot
```

### Small Mesh

```{r}
`YELGB_SQUID/WHITING`$plot
```

### Other

```{r}
YELGB_OTHER$plot
```

# SNE Yellowtail

## Sector

```{r}
YELSNE_SECT$plot
```

### Common Pool

```{r}
YELSNE_CP$plot  
```

### Scallop

```{r}
YELSNE_SCALLOP$plot
```

### State

```{r}
YELSNE_STATE$plot
```

### Other

```{r}
YELSNE_OTHER$plot
```

# GB Winter Flounder

### Groundfish

```{r}
FLWGB_GROUND$plot
```

### Other

```{r}
FLWGB_OTHER$plot
```

# SNE Winter Flounder

### Sector

```{r}
FLWSNEMA_SECT$plot
```

### Common Pool

```{r}
FLWSNEMA_CP$plot
```

### State

```{r}
FLWSNEMA_STATE$plot
```

### Other

```{r}
FLWSNEMA_OTHER$plot
```

# White Hake

### Sector

```{r}
HKWGMMA_SECT$plot
```

### Common Pool

```{r}
HKWGMMA_CP$plot
```

### State

```{r}
HKWGMMA_STATE$plot
```

### Other

```{r}
HKWGMMA_OTHER$plot
```

# Acadian Redfish

## Sector

```{r}
REDGMGBSS_SECT$plot
```

### Common Pool

```{r}
REDGMGBSS_CP$plot
```

### State

```{r}
REDGMGBSS_STATE$plot
```

### Other

```{r}
REDGMGBSS_OTHER$plot
```

